% ============================================================================
% BÁO CÁO ĐỀ TÀI: FastViT - A Fast Hybrid Vision Transformer
%                  using Structural Reparameterization
% ============================================================================
\documentclass[12pt, a4paper]{report}

% --- Encoding & Language ---
\usepackage[utf8]{inputenc}
\usepackage[vietnamese]{babel}
\usepackage{vntex}

% --- Page Layout ---
\usepackage[top=2.5cm, bottom=2.5cm, left=3cm, right=2cm]{geometry}
\usepackage{setspace}
\onehalfspacing

% --- Math & Symbols ---
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{mathtools}
\usepackage{bm}

% --- Graphics & Figures ---
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage[font=small, labelfont=bf]{caption}

% --- Tables ---
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{colortbl}

% --- Colors ---
\usepackage[dvipsnames, table]{xcolor}

% --- Code Listings ---
\usepackage{listings}
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    commentstyle=\color{ForestGreen},
    stringstyle=\color{red},
    numbers=left,
    numberstyle=\tiny\color{gray},
    numbersep=8pt,
    breaklines=true,
    frame=single,
    backgroundcolor=\color{gray!5},
    tabsize=4,
    showstringspaces=false,
}

% --- Algorithms ---
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}

% --- Hyperlinks & References ---
\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
\usepackage{bookmark}

% --- Bibliography ---
\usepackage[numbers, sort&compress]{natbib}

% --- Misc ---
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{tikz}
\usetikzlibrary{shapes, arrows, positioning, calc, fit, backgrounds}
\usepackage{pgfplots}
\pgfplotsset{compat=1.17}

% --- Custom Commands ---
\newcommand{\repmixer}{\textsc{RepMixer}}
\newcommand{\fastvit}{\textsc{FastViT}}
\newcommand{\vit}{\textsc{ViT}}
\newcommand{\resnet}{\textsc{ResNet}}
\newcommand{\vgg}{\textsc{VGG}}
\newcommand{\convnext}{\textsc{ConvNeXt}}
\newcommand{\repvgg}{\textsc{RepVGG}}
\newcommand{\bigO}[1]{\mathcal{O}\left(#1\right)}

% --- Header/Footer ---
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\leftmark}
\fancyhead[R]{\small\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% ============================================================================
% DOCUMENT
% ============================================================================
\begin{document}

% --- Title Page ---
\begin{titlepage}
\begin{center}

\vspace*{1cm}
{\Large\textbf{TRƯỜNG ĐẠI HỌC}}\\[0.3cm]
{\Large\textbf{KHOA CÔNG NGHỆ THÔNG TIN}}\\[2cm]

\rule{\linewidth}{0.5mm}\\[0.5cm]
{\LARGE\textbf{BÁO CÁO ĐỒ ÁN}}\\[0.3cm]
{\Huge\textbf{FastViT: A Fast Hybrid Vision Transformer\\using Structural Reparameterization}}\\[0.3cm]
\rule{\linewidth}{0.5mm}\\[2cm]

{\large\textbf{Ngành:} Công nghệ Thông tin}\\[0.3cm]
{\large\textbf{Chuyên ngành:} Trí tuệ Nhân tạo / Thị giác Máy tính}\\[2cm]

\vfill
{\large Năm 2025}

\end{center}
\end{titlepage}

% --- Table of Contents ---
\tableofcontents
\newpage

% --- List of Figures ---
\listoffigures
\newpage

% --- List of Tables ---
\listoftables
\newpage

% --- Chapters ---
\input{chapters/chapter1_introduction}
\input{chapters/chapter2_background}
\input{chapters/chapter3_architecture}
\input{chapters/chapter4_experiment_setup}
\input{chapters/chapter5_results}
\input{chapters/chapter6_conclusion}

% --- Bibliography ---
\bibliographystyle{plainnat}
\begin{thebibliography}{99}

\bibitem{fastvit2023}
P.~K.~A. Vasu, J.~Gabriel, J.~Zhu, O.~Tuzel, and A.~Ranjan.
\newblock Fast{V}i{T}: A fast hybrid vision transformer using structural reparameterization.
\newblock In \emph{Proceedings of the IEEE/CVF International Conference on Computer Vision (ICCV)}, 2023.

\bibitem{vgg2015}
K.~Simonyan and A.~Zisserman.
\newblock Very deep convolutional networks for large-scale image recognition.
\newblock In \emph{ICLR}, 2015.

\bibitem{resnet2016}
K.~He, X.~Zhang, S.~Ren, and J.~Sun.
\newblock Deep residual learning for image recognition.
\newblock In \emph{CVPR}, pages 770--778, 2016.

\bibitem{repvgg2021}
X.~Ding, X.~Zhang, N.~Ma, J.~Han, G.~Ding, and J.~Sun.
\newblock Rep{VGG}: Making {VGG}-style conv{N}ets great again.
\newblock In \emph{CVPR}, pages 13733--13742, 2021.

\bibitem{vit2021}
A.~Dosovitskiy, L.~Beyer, A.~Kolesnikov, D.~Weissenborn, X.~Zhai, T.~Unterthiner, M.~Dehghani, M.~Minderer, G.~Heigold, S.~Gelly, J.~Uszkoreit, and N.~Houlsby.
\newblock An image is worth 16x16 words: Transformers for image recognition at scale.
\newblock In \emph{ICLR}, 2021.

\bibitem{convnext2022}
Z.~Liu, H.~Mao, C.~Wu, C.~Feichtenhofer, T.~Darrell, and S.~Xie.
\newblock A conv{N}et for the 2020s.
\newblock In \emph{CVPR}, pages 11976--11986, 2022.

\bibitem{transformer2017}
A.~Vaswani, N.~Shazeer, N.~Parmar, J.~Uszkoreit, L.~Jones, A.~N. Gomez, L.~Kaiser, and I.~Polosukhin.
\newblock Attention is all you need.
\newblock In \emph{NeurIPS}, pages 5998--6008, 2017.

\bibitem{mobileone2023}
P.~K.~A. Vasu, J.~Gabriel, J.~Zhu, O.~Tuzel, and A.~Ranjan.
\newblock Mobile{O}ne: An improved one millisecond mobile backbone.
\newblock In \emph{CVPR}, 2023.

\bibitem{depthwise2017}
A.~G. Howard, M.~Zhu, B.~Chen, D.~Kalenichenko, W.~Wang, T.~Weyand, M.~Andreetto, and H.~Adam.
\newblock Mobile{N}ets: Efficient convolutional neural networks for mobile vision applications.
\newblock \emph{arXiv preprint arXiv:1704.04861}, 2017.

\bibitem{replknet2022}
X.~Ding, X.~Zhang, J.~Han, and G.~Ding.
\newblock Scaling up your kernels to 31x31: Revisiting large kernel design in {CNN}s.
\newblock In \emph{CVPR}, 2022.

\bibitem{metaformer2022}
W.~Yu, M.~Luo, P.~Zhou, C.~Si, Y.~Zhou, X.~Wang, J.~Feng, and S.~Yan.
\newblock Meta{F}ormer is actually what you need for vision.
\newblock In \emph{CVPR}, 2022.

\bibitem{imagenet2009}
J.~Deng, W.~Dong, R.~Socher, L.-J. Li, K.~Li, and L.~Fei-Fei.
\newblock Image{N}et: A large-scale hierarchical image database.
\newblock In \emph{CVPR}, pages 248--255, 2009.

\bibitem{se2018}
J.~Hu, L.~Shen, and G.~Sun.
\newblock Squeeze-and-excitation networks.
\newblock In \emph{CVPR}, pages 7132--7141, 2018.

\bibitem{focalloss2017}
T.~Lin, P.~Goyal, R.~Girshick, K.~He, and P.~Doll{\'a}r.
\newblock Focal loss for dense object detection.
\newblock In \emph{ICCV}, pages 2980--2988, 2017.

\end{thebibliography}

\end{document}
